---
title: "Individual Project 2"
author: "Drake Francis M. Jaculina"
date: "`r Sys.Date()`"
output: html_document
---

### Packages
```{r, }
library(dplyr) 
library(tidyr) 
library("plotly") 
library(ggplot2) 
library(RColorBrewer) 
library(tidytext) 
library(rtweet)  
library(tm) 
library(slam)
library(wordcloud) 
library(wordcloud2) 
library(corpus) 
library('twitteR')
```

### Set-up credentials
```{r, }
CONSUMER_SECRET <- "EgBXGhnnkfO89aMo4kgcK7PTEUWkb8iuBVH2MQ6Vtvnz4lvq5d"
CONSUMER_KEY <- "2AgsJ1H0uR91Rszh4Jy7b3ywF"
ACCESS_SECRET <- "vnAXimpZEAkBaZ1FSBgYkspw5Fp5xIb62ea1o93V6x9eH"
ACCESS_TOKEN <- "1592627451393617920-Hy59KCLtTj0Fk6IDqAa33zx1O86fI3"
```

### connect to twitter app
```{r, }
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```

### Extract 10000 tweets from Twitter using twitteR package including retweets.
```{r, }
trend_BLSERIES_Tweets <- searchTwitter("BL",
                                   n = 10000,
                                   lang = "en",
                                   since = "2022-11-10",
                                   until = "2022-11-30",
                                   retryOnRateLimit=120)
trend_BLSERIES_Tweets
```

### Convert data into data frame
```{r, }
trend_BLSERIES_TweetsDF <- twListToDF(trend_BLSERIES_Tweets)
trend_BLSERIES_TweetsDF
```

### Save data frame as a .Rdata file
```{r, }
save(trend_BLSERIES_TweetsDF,file = "trend_BLSERIES_TweetsDF.Rdata")
```

### Load
```{r, }
load(file = "trend_BLSERIES_TweetsDF.Rdata")
```

### Checking for missing values.
```{r, }
sap_data <- sapply(trend_BLSERIES_TweetsDF, function(x) sum(is.na(x)))
sap_data
```

### Subset the retweets and the original tweets into a separate file using the dplyr()package.
```{r, }
TRUE_isRetweet_BLSERIES <- trend_BLSERIES_TweetsDF %>%
  select(screenName,text,created,statusSource,isRetweet) %>%
  filter(isRetweet == "TRUE")
TRUE_isRetweet_BLSERIES

  #Save as a .Rdata file
save(TRUE_isRetweet_BLSERIES,file = "TRUE_isRetweet_BLSERIES.Rdata")

FALSE_isRetweet_BLSERIES <- trend_BLSERIES_TweetsDF %>%
  select(screenName,text,created,statusSource,isRetweet) %>%
  filter(isRetweet == "FALSE")
FALSE_isRetweet_BLSERIES

  #Save as a .Rdata file
save(TRUE_isRetweet_BLSERIES,file = "FALSE_isRetweet_BLSERIES.Rdata")
```

### Plot the retweets and the original tweets using bar graph in vertical manner Include legends

### Grouping the TRUE_isRetweet_BLSERIES.
```{r, }
TRUE_isRetweet_BLSERIES %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

CREATED_DATA <- TRUE_isRetweet_BLSERIES %>% mutate(Created_At_Round = created %>% round(units = 'hours') %>% as.POSIXct())
CREATED_DATA

#Plotting
TRUE_DATA <- ggplot(CREATED_DATA, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of Retweets") + 
  scale_fill_gradient(low = "#132B43", high = "#56B1F7", space = "Lab",
                      na.value = "grey50", guide = "colourbar", aesthetics = "fill")

TRUE_DATA %>% ggplotly()
```

### Grouping the FALSE_isRetweet_BLSERIES. 
```{r, }
FALSE_isRetweet_BLSERIES %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))

CREATED_DATA2 <- FALSE_isRetweet_BLSERIES %>% mutate(Created_At_Round = created %>% round(units = 'hours') %>% as.POSIXct())
CREATED_DATA2

#Plotting
TRUE_DATA2 <- ggplot(CREATED_DATA2, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of Tweets") + 
  scale_fill_gradient(low = "#132B43", high = "#56B1F7", space = "Lab",
                    na.value = "grey50", guide = "colourbar", aesthetics = "fill")

TRUE_DATA2 %>% ggplotly()
```
