---
title: "Worksheet-6 in R"
author: "Drake Francis M. Jaculina"
date: "`r Sys.Date()`"
output: pdf_document
---

## Use the dataset mpg
```{r,}
library(ggplot2)
library(dplyr)
library(tidyverse)
data(mpg)
as.data.frame(data(mpg))
str(mpg)
```

## Use of glimpse() - much tidier compared to str()
```{r,}
glimpse(mpg)
```

## Example. graph using ggplot()
```{r,}
ggplot(mpg, aes(cty, hwy)) +
  geom_point()
```

### 1. How many columns are in mpg data set? How about the number of rows? Show the codes and its result.
```{r,}
#Number of columns in mpg data set
mpg_col <- ncol(mpg)
mpg_col
#Number of rows in mpg data set
mpg_row <- nrow(mpg)
mpg_row
#Ans: There are 11 columns and 234 rows in the mpg data set.
```

### 2. Which manufacturer has the most models in this data set? Which model has the most variations?
```{r,}
manuf_count <- mpg %>% group_by(manufacturer) %>% tally (sort = TRUE)
manuf_count
colnames(manuf_count)<-c("Manufacturer", "Counts")

#Ans: dodge is the manufacturer has the most models in this data set which has 37 models.
```

### a. Group the manufacturers and find the unique models. Copy the codes and result.
```{r,}
unique_manuf <- mpg %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
colnames(unique_manuf) <- c("Manufacturer", "Model","Counts")
unique_manuf
```

### b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r,}
#plot()
plot(unique_manuf)
#ggplot()
ggplot(unique_manuf, aes(Model, Manufacturer)) + geom_point()
```

### 3. Same dataset will be used. You are going to show the relationship of the model and the manufacturer.

### a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r,}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

### b. For you, is it useful? If not, how could you modify the data to make it more informative?
```{r,}
#Ans: It is not useful, It's already informative but you can't see the ranking or the hierarchy of the given data and some of the data is hidden. I could modify the data to make it more informative using `geom_bar()` and adding legend.
```

### 4. Using the pipe (%>%), group the model and get the number of cars per model. Show codes and its result.
```{r,}
group_model <- unique_manuf %>% group_by(Model) %>% count()
group_model
colnames(group_model) <- c("Model","Counts")
group_model
```

### a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result.
```{r,}
qplot(model,data = mpg,main = "Number of Cars per Model", xlab = "Model",ylab = "Number
of Cars", geom = "bar", fill = manufacturer) + coord_flip()
```

### b. Use only the top 20 observations. Show code and results.
```{r,}
twenty_obser <- group_model[1:20,] %>% top_n(2)
twenty_obser
#Using ggplot()
ggplot(twenty_obser,aes(x = Model, y = Counts)) + geom_bar(stat = "Identity") +coord_flip()
```

### 5. Plot the relationship between cyl - number of cylinders and displ - engine displace-ment using geom_point with aesthetic colour = engine displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.

### a. Show the codes and its result.
```{r,}
ggplot(data = mpg, mapping = aes(x = displ, y = cyl, main = "Relationship between No. of Cylinders and Engine Displacement")) +
  geom_point(mapping=aes(colour = "engine displacement"))
```

### b. How would you describe its relationship?
```{r,}
#Ans: We can see that the the scatter plot it has 3 clustered data, the more number of cylinder increase the more engine displacement increases or expand.
```

### 6. Get the total number of observations for drv - type of drive train (f = front-wheel drive, r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.). Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.

### a. Show the codes and its result for the narrative in #6.
```{r,}
ggplot(data = mpg, mapping = aes(x = drv, y = class)) + geom_tile(aes(fill=class))
```

### b. Interpret the result.
```{r,}
#Ans: The result of given data is that it shows the class and drv. subcompact has all the drv which include the 4, f, and r. Midsize and compact has the same class which under the 4 wheeler drive, suv composed only of 4 and r in drv. Pickup has only 1 drv which the 4 wheeler drive, minivan results to have drv of f, and also the 2seater with drv of r only.
```

### 7. Discuss the difference between these codes. Its outputs for each are shown below.

#### Code #1
```{r,}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

#### Code #2
```{r,}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```

```{r,}
#Ans: The given codes are mostly the same but it has slight differences. The code #1, colour = "blue" is enclosed with mapping and aesthetic. The result doesn't change into blue but instead gave us color red. While code #2 the colour = "blue" is not enclosed with the mapping and aesthetic. The result it show us that the color of the graph is blues. Because of the code #1 of this it was a interpreted as a categoral variable or as a group.
```

### 8. Try to run the command ?mpg. What is the result of this command?
```{r,}
?mpg
#Ans: The result of this command it will go to the Help pane and it will allow us to see or access the documentation on a particular function of mpg.
```

### a. Which variables from mpg dataset are categorical?
```{r,}
#Ans: manufacturer, model, trans, drv, fl, and class.
```

### b. Which are continuous variables?
```{r,}
#Ans: displ, year, cyl, cty, and hwy.
```

### c. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in #5-b. What is its result? Why it produced such output?
```{r,}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()
```

### 9. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon) using geom_point(). Add a trend line over the existing plot using geom_smooth() with se = FALSE. Default method is “loess”.
```{r,}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_point(mapping=aes(color=class))+ 
  geom_smooth(se = FALSE, method = loess)
```

### 10. Using the relationship of displ and hwy, add a trend line over existing plot. Set the se = FALSE to remove the confidence interval and method = lm to check for linear modeling.
```{r,}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) + geom_point() +
  geom_smooth(se = FALSE, method = lm)
```